PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-03-31 manuscript_00.Rmd

library(pool)
library(RSQLite)
meta_filter_v0 <- fst::read_fst("/Volumes/McGaughey_S/scEiaD/paper_data/2021_03_17_meta_filter.fst") %>% 
  mutate(CellType_predict = case_when(CellType_predict == 'AC/HC_Precurs' ~ 'AC/HC Precursor',
                                      TRUE ~ CellType_predict),
         CellType= case_when(CellType == 'AC/HC_Precurs' ~ 'AC/HC Precursor',
                             TRUE ~ CellType))
# remove eric bharti 2D/3D RPE
meta_filter <- fst::read_fst("~/data/scEiaD_2022_02/meta_filter.fst") %>% filter(study_accession != 'Bharti_Nguyen_iRPE_2D_3D') %>% 
  mutate(CellType_predict = case_when(CellType_predict == 'AC/HC_Precursor' ~ 'AC/HC Precursor',
                                      TRUE ~ CellType_predict),
         CellType= case_when(CellType == 'AC/HC_Precursor' ~ 'AC/HC Precursor',
                             TRUE ~ CellType),  
         Tissue = case_when(grepl('Iris', Tissue) ~ 'Iris',
                            TRUE ~ Tissue))

>>>>

library(pool)
library(RSQLite)
meta_filter_v0 <- fst::read_fst(glue("{data_dir_vGiga}/paper_data/2021_03_17_meta_filter.fst")) %>%

  mutate(CellType_predict = case_when(CellType_predict == 'AC/HC_Precurs' ~ 'AC/HC Precursor',
                                      TRUE ~ CellType_predict),
         CellType= case_when(CellType == 'AC/HC_Precurs' ~ 'AC/HC Precursor',
                             TRUE ~ CellType))

meta_filter <- fst::read_fst(glue("{data_dir_vPLAE}/meta_filter.fst")) %>% filter(study_accession != 'Bharti_Nguyen_iRPE_2D_3D') %>%

  mutate(CellType_predict = case_when(CellType_predict == 'AC/HC_Precursor' ~ 'AC/HC Precursor',
                                      TRUE ~ CellType_predict),
         CellType= case_when(CellType == 'AC/HC_Precursor' ~ 'AC/HC Precursor',
                             TRUE ~ CellType),  
         Tissue = case_when(grepl('Iris', Tissue) ~ 'Iris',
                            TRUE ~ Tissue),

         Citation = case_when(study_accession == 'OGVFB_Hufnagel_iPSC_RPE' ~ 'Swamy VS, Fufa TD, Hufnagel RB, McGaughey DM Building the Mega Single Cell Transcriptome Ocular Meta-Atlas Gigascience 2021 Oct 13;10(10)',
                              TRUE ~ Citation),
         PMID = case_when(study_accession == 'OGVFB_Hufnagel_iPSC_RPE' ~ '34651173',
                          TRUE ~ PMID),
         study_accession = case_when(study_accession == 'OGVFB_Hufnagel_iPSC_RPE' ~ 'SRP329495',
                                     TRUE ~ study_accession))
